---
title: "Lab 03-Not Team One"
author: "David Orozco, Anderson Mun, Arie de Valle, Ethan Schacht"
date: "January 30, 2019"
output: html_document
---
****
### Individual Component:
*****
#### David's Graph
```{r,  echo = FALSE, message = FALSE}
library(tidyverse)
source("http://www.openintro.org/stat/data/cdc.R")
cdc <- as_tibble(cdc)

```
```{r,  echo = FALSE, message = FALSE}
ggplot(data = cdc, mapping = aes(x = age))+
  geom_density(color = "black") +
  ggtitle("Health Distribution Based on Age") +
facet_grid(genhlth ~ smoke100)
```

* The graph above shows the distribution of age depending on a two parameters.There parameters are general health classification and wether an individual smokes. The first column (labeled '0') are non-smokers and the second are smokers. Each box is the age distribution of people who meet the parameters in their location. 

****
#### Anderson's Graph

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
ggplot(data = cdc, mapping = aes(x = age, y = exerany, color = genhlth)) +
  geom_smooth(se = FALSE) +
  ggtitle("General Health and Exercise vs. Age")
```

* Insert text about what the graph shows here

****
#### Arie's Graph
```{r ggplot, echo = FALSE, message = FALSE}

ggplot(data = cdc)+
  geom_bar(mapping = aes(x = genhlth, fill = gender), color = "black", position = "dodge")+
  xlab("General Health Condition")+
  ylab("Number of People")+
  ggtitle("General Health of Males vs. Females")+
  theme(plot.title = element_text(hjust = .5))


```

* Insert text about what the graph shows here

****
#### Ethan's Graph
****
### Team Component:
*****
#### Team Graph
 
```{r,  echo = FALSE, message = FALSE} 
ggplot(data = cdc) + 
  geom_bar(mapping = aes(x = smoke100, fill = genhlth),position = "dodge")+ 
  facet_grid(.~gender) + 
  ggtitle("General Health of Smokers vs. Nonsmokers") + 
  xlab("Smoke (1 = yes, 0 = no)") 
 
```

* Insert text about what the graph shows here